Measuring sustainability with Australian vine growers using a Bayesian Network

### 2023-10-31 article.tex
adding reference recomendation to methods.
added list of definitions and minor update sto article

\section{Methods}

% These are transcribed notes from Korb & Nicholson:

@@

Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroberated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.

>>>>

\section{Methods}
\citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
% These are transcribed notes from Korb & Nicholson:

@@

Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
